Cover Letter

### 2017-12-22 paper/sections/3_posix_overheads.tex
paper: fix graphs and add baselines (#33, #34)
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>
paper: fix graphs
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure}[tb]
\centering
\includegraphics[width=1\linewidth]{./graphs/overhead-creates.png}

\caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/baseline-compile/visualize/viz.ipynb}{source}]
Create-heavy workloads (such as \texttt{untar}) incur the highest disk,
network, and CPU utilization because of the consistency and durability demands
of CephFS.}\label{fig:overhead-creates}

\end{figure}

@@

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=0.95\linewidth]{graphs/slowdown-journal.png}
      \caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/baseline-durability/visualize/viz.ipynb}{source}]
      Effect of Journal} \label{fig:overhead-a}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.1\linewidth]{graphs/behavior-interfere.png}
      \caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/baseline-interfere/visualize/viz.ipynb}{source}]
      Interference increases RPCs}
      \label{fig:overhead-b}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1\linewidth]{graphs/slowdown-interfere-scale.png}
      \caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/baseline-creates/visualize/viz.ipynb}{source}]
      Interference hurts variability}
      \label{fig:overhead-c}
  \end{subfigure}
  \caption{ The overhead of durability and strong consistency in CephFS.  (a)
  shows the effect of different journal segment sizes, normalized to a setup
  without a journal (``No Journal").  The journal is streamed into the object
  store for fault tolerance. (b) and (c) show that when a second client
  ``interferes", capabilities are revoked and metadata servers do more work.
  \label{fig:overhead}}
\end{figure*}

@@

% - sequential IO, trim redundant operations
\textbf{CephFS Design}: A journal of metadata updates that streams into the
resilient object store. Similar to LFS~\cite{rosenblum:acm1992-LFS} and
WAFL~\cite{hitz:wtec1994-WAFL} the metadata journal is designed to be large
(on the order of MBs) which ensures (1) sequential writes into the object store
and (2) the ability for daemons to trim redundant or irrelevant journal
entries.  The journal is striped over objects where multiple journal updates
can reside on the same object. There are two tunables for controlling the
journal: the segment size and the number of segments that can be written in
parallel. Unless the journal saturates memory or CPU resources, larger values
for these tunables results in better performance.

@@

% Effects on performance
Figure~\ref{fig:overhead-a} shows the effect of journaling of with different
segment sizes; the larger the segment size the bigger that the writes into the
object store are. The trade-off for better performance is memory consumption
because larger segments take up more space for buffering. When journaling is
on, the metadata server periodically stops serving requests to flush ({\it
i.e.} apply journal updates) to the metadata store.  The journal overhead is
sufficient enough to slow down metadata throughput but not so much as to
overwhelm the bandwidth of the object store.

@@

% benefits PROBLEM -- IS THIS THE METADATA PROTOCOL OR JUST THE OVERLOADEDNESS?
The benefits of caching the directory inode when creating files is shown in
Figure~\ref{fig:overhead-b}. The colors show the behavior of the client for two
different runs.  If only one client is creating files in a directory
(``isolated" curve on \(y1\) axis) then that client can lookup the existence of
new files locally before issuing a create request to the metadata server. If
another client starts creating files in the same directory then the directory
inode transitions out of read caching and the first client must send
\texttt{lookup()}s to the metadata server (``interfere" curve on \(y2\) axis).
These extra requests increase the throughput of the ``interfere" curve on the
\(y1\) axis because the metadata server can handle the extra load but
performance suffers.  This degradation is shown in Figure~\ref{fig:overhead-c},
where we scale the number of clients and show the slowdown of the slowest
client.  The results are normalized to a single isolated client without a
metadata server journal and the error bars are the standard deviations of all
client runtimes.  For the ``interfere" bars, each client creates files in
private directories and at 30 seconds we launch another process that creates
files in those directories. 18 is the maximum number of clients the metadata
server can handle for this metadata-intensive workload; at higher client load,
the metadata server complains about laggy and unresponsive requests.

>>>>

\begin{figure}[tb]
\centering
\includegraphics[width=1\linewidth]{./graphs/overhead-creates.png}
\caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/baseline-compile/visualize/viz.ipynb}{source}]
Create-heavy workloads (such as \texttt{untar}) incur the highest disk,
network, and CPU utilization because of the consistency and durability demands
of CephFS.}\label{fig:overhead-creates}
\end{figure}

@@

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1\linewidth]{graphs/slowdown-journal.png}
      \caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/baseline-durability/visualize/viz.ipynb}{source}]
      effect of journal} \label{fig:overhead-a}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=0.98\linewidth]{graphs/slowdown-interfere-scale.png}
      \caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/baseline-creates/visualize/viz.ipynb}{source}]
      interference hurts variability}
      \label{fig:overhead-b}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.1\linewidth]{graphs/behavior-interfere.png}
      \caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/baseline-interfere/visualize/viz.ipynb}{source}]
      interference increases RPCs}
      \label{fig:overhead-c}
  \end{subfigure}

  \caption{\newcomment{The durability and strong consistency slowdown of the
existing CephFS implementation increases as the number of clients scales.
Results are normalized to 1 client that creates 100K files in isolation.  (a)
shows the effect of journaling metadata updates; ``segment(s)" is the number
of journal segments dispatched to disk at once. (b) shows the slowdown when
another client interferes by creating files in all directories and (c)
highlights the cause: }\oldcomment{The overhead of durability and strong
consistency in CephFS. (a) shows the effect of different journal segment sizes,
which are streamed into the object store for fault tolerance. (b) and (c) show
that} when another client ``interferes", capabilities are revoked and metadata
servers do more work.} \label{fig:overhead}

\end{figure*}

@@

% - sequential IO, trim redundant operations
\textbf{CephFS Design}: A journal of metadata updates that streams into the
resilient object store. Similar to LFS~\cite{rosenblum:acm1992-LFS} and
WAFL~\cite{hitz:wtec1994-WAFL} the metadata journal is designed to be large (on
the order of MBs) which ensures (1) sequential writes into the object store and
(2) the ability for daemons to trim redundant or irrelevant journal entries.
The journal is striped over objects where multiple journal updates can reside
on the same object. There are two tunables\newcomment{, related to groups of
journal events called segments,} for controlling the journal: the segment size
and the dispatch size ({\it i.e.} the number of segments that can be dispatched
at once).  Unless the journal saturates memory or CPU resources, larger values
for these tunables results in better performance.

@@

% Effects on performance
Figure~\ref{fig:overhead-a} shows the effect of journaling with different
\oldcomment{segment sizes; the larger the segment size the bigger that the
writes into the object store are}\newcomment{dispatch sizes, normalized to 1
client that creates 100K files with journaling off (about 654 creates/sec). In
this case a dispatch size of 10 degrades performance more because the metadata
server is overloaded with requests and cannot spare cycles to manage concurrent
segments.  Although the ``no journal" curve appears flat, it is actually a
slowdown of about \(0.3\times\) per concurrent client; this slowdown is a
result of the peak throughput of a single metadata server, which we found to be
about 3000 operations per second}.  The trade-off for better performance is
memory consumption because a larger \oldcomment{segment}\newcomment{dispatch}
size uses more space for buffering.  When journaling is on, the metadata server
periodically stops serving requests to flush ({\it i.e.} apply journal updates)
to the metadata store.  The journal overhead is sufficient enough to slow down
metadata throughput but not so much as to overwhelm the bandwidth of the object
store.

@@

% benefits PROBLEM -- IS THIS THE METADATA PROTOCOL OR JUST THE OVERLOADEDNESS?
\oldcomment{This degradation is shown in Figure~\ref{fig:overhead-b}, where we
scale the number of clients and show the slowdown of the slowest client.  The
results are normalized to a single isolated client without a metadata server
journal and the error bars are the standard deviations of all client runtimes.}
\newcomment{Figure~\ref{fig:overhead-b} shows the slowdown of maintaining
strong consistency when scaling the number of clients.  We plot the slowdown of
the slowest client, normalized to 1 client that creates 100K files (about 513
creates/sec because the journal is turned back on).} For the ``interference"
curve, each client creates files in private directories and at 30 seconds we
launch another process that creates files in those directories. \oldcomment{18
is}\newcomment{20 clients has an asterisk\* because} the maximum number of
clients the metadata server can handle for this metadata-intensive workload
\newcomment{is actually 18}; at higher client load, the metadata server
complains about laggy and unresponsive requests.

\oldcomment{The benefits of caching the directory inode when creating
files}\newcomment{The cause for this slowdown} is shown in
Figure~\ref{fig:overhead-c}. The colors show the behavior of the client for two
different runs.  If only one client is creating files in a directory
(``isolated" curve on \(y1\) axis) then that client can lookup the existence of
new files locally before issuing a create request to the metadata server. If
another client starts creating files in the same directory then the directory
inode transitions out of read caching and the first client must send
\texttt{lookup()}s to the metadata server (``interfere" curve on \(y2\) axis).
These extra requests increase the throughput of the ``interfere" curve on the
\(y1\) axis because the metadata server can handle the extra load but
performance suffers.

### 2017-12-22 paper/sections/6_results.tex
paper: fix graphs
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/mergescale.png}
      \caption{\texttt{create}: done in parallel on clients}
      \label{fig:mergescale}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/block-allow.png}
      \caption{Subtree semantics: block interference}
      \label{fig:block-allow}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-sync.png}
      \caption{Syncing to global namespace}
      \label{fig:slowdown-sync}
  \end{subfigure}
\caption{ The performance and features of Cudele. (a)
[\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/cudele-mergescale/visualize/viz.ipynb}{source}]
shows the cost of merging client journals at the metadata server. Shipping and
merging journals of updates scales better than RPCs because there are less
messages and consistency/durability code paths are bypassed. (b)
[\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/cudele-blockapi/visualize/viz.ipynb}{source}]
the allow/block API isolates directories from interfering clients. (c)
[\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/cudele-partialreads/visualize/viz.ipynb}{source}]
is the slowdown of a single client syncing updates to the global namespace. The
inflection point is the trade-off of frequent updates vs. larger journal
files.} \label{fig:use-cases}
\end{figure*}

>>>>

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/mergescale.png}
      \caption{
      [\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/cudele-mergescale/visualize/viz.ipynb}{source}]
      \newcomment{parallel creates on clients}
      }\label{fig:mergescale}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/block-allow.png}
      \caption{
      [\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/cudele-blockapi/visualize/viz.ipynb}{source}]
      \newcomment{block interference}
      }\label{fig:block-allow}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-sync.png}
      \caption{
      [\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/cudele-partialreads/visualize/viz.ipynb}{source}]
      \newcomment{syncing to global namespace}
      }\label{fig:slowdown-sync}
  \end{subfigure}
\caption{\oldcomment{ The performance and features of Cudele}\newcomment{Cudele
performance}. (a) \newcomment{shows the speedup of decoupled namespaces over
RPCs; \texttt{create} is the throughput of clients creating files in-parallel
and writing updates locally; \texttt{create+merge} includes the time to merge
updates at the metadata server. }\oldcomment{shows the cost of merging client
journals at the metadata server. Shipping and merging journals of
updates}\newcomment{Decoupled namespaces} scale better than RPCs because there
are less messages and consistency/durability code paths are bypassed. (b) shows
how the allow/block API isolates directories from interfering clients. (c) is
the slowdown of a single client syncing updates to the global namespace. The
inflection point is the trade-off of frequent updates vs. larger journal
files.}
\label{fig:use-cases}
\end{figure*}
